Parallel Global Optimization for Non-Convex Mixed-Integer Problems \thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2019-04-11 2019/RSD_Integer/RSD2019.tex
Semi-final

The paper considers the mixed-integer global optimization problems. A novel 
parallel algorithm for solving the problems of this class based on the index 
algorithm to solving the continuous global optimization problems has been proposed. 
The comparison of this algorithm with known analogs demonstrates the efficiency of the 
developed approach. 
%Russian
The proposed algorithm allows an efficient parallelization including the employment of the 
graphics accelerators. The results of performed numerical experiments (solving a series of 100 multiextremal mixed-integer problems) confirm a good speedup of the algorithm with the use of GPU.

@@

In this paper the global optimization problems and the method of solving these ones are 
considered. The global optimization problems are the time-consuming ones since the global 
optimum is an integral characteristic of the problem being solved and requires the investigation 
of the whole search domain. 
As a result, the search of the global optimum is reduced to the construction of a coverage (in 
general, a nonuniform one) of the space of parameters. 
The problems, in which some parameters can take the discrete or integer values only (mixed-integer global 
optimization problems) are of special interest because for these problems it is more difficult to build 
the estimates of the optimum as compared to the continuous ones.

@@

As an illustration, Fig. \ref{fig:1} presents the plots of the functions corresponding to a 
problem 
\[
%\min{\left\{ x^2 - 10\cos(2\pi x) + u^2 - 10\cos(2\pi u) : x\in [-2.22, 1.8], u \in {0,1} \right\}}
\min{\left\{ u^2 (\sin(x) +\sin(10x/3) : x\in [2.7, 7.5], u \in \{1,2\} \right\}}
\]
with one continuous parameter $x$ and one binary parameter $u$.
%Еще один график?

@@

\begin{enumerate}
	\item A continuous multiextremal function $\varphi(y), y\in D = \left\{ a_j\leq 
y_j\leq b_j, 1\leq j \leq N \right\}$ is generated with the use of the GKLS generator. The global 
minimum of this function is achieved at the known point $y'=(y'_1,...,y'_N)$ and equals 
$\varphi(y')=-1$.
	\item A concave mixed-integer function 
	\[
			h(y,u) = -2 \left[ \sum_{j=1}^N \left( \frac{y_j - y'_j}{b_j-a_j} 
\right)^2 + \sum_{j=1}^M \left( \frac{u_j - b_j}{b_j-a_j} \right)^2 \right],
	\]
	is generated where 
	\begin{gather}
	y\in D = \left\{ a_j\leq y_j\leq b_j, 1\leq j \leq N \right\} \subset R^N,\nonumber \\
	u\in U = \left\{ u_j \in  \left\{a_j, ..., b_j \right\}, 1\leq j \leq M \right\}.\nonumber
	\end{gather}
	This function has $N$ continuous and $M$ discrete parameters and achieves its 
minimum value at the point $(y',b)$.
	\item The coefficient 
	\[
	h_{min} = 4 - \min_{y,u} \left\{ h(y,u) \right\}, \; y\in D, u \in U.
	\]
	is computed. 
It is obvious, that the minimum of a concave function $\mu(y,u)$ is located at one of the corner 
points of the search domain. Therefore, if the problem dimensionality is of the order of 10 it can 
be found by the brute force method.
	\item A multiextremal mixed-integer function 
	\[
	f(y,u) = \left(\varphi(y) + \sum_{j=1}^M{u_j}\right)\left(h_{min} + h(y,u)\right).
	\]
	is formed.
By construction, $f(y,u)$ would take its minimum value at the point $(y',b)$.

>>>>

The paper considers the mixed-integer global optimization problems. A novel 
parallel algorithm for solving the problems of this class based on the index 
algorithm for solving the continuous global optimization problems has been proposed. 
The comparison of this algorithm with known analogs demonstrates the efficiency of the 
developed approach. 
%Russian
The proposed algorithm allows an efficient parallelization including the employment of the 
graphics accelerators. The results of performed numerical experiments (solving a series of 100 multiextremal mixed-integer problems) confirm a good speedup of the algorithm with the use of GPU.

@@

In this paper the global optimization problems and the method of their solving are 
considered. The global optimization problems are the time-consuming ones since the global 
optimum is an integral characteristic of the problem being solved and requires the investigation 
of the whole search domain. 
As a result, the search of the global optimum is reduced to the construction of a coverage (in 
general, a nonuniform one) of the space of parameters. 
The problems, in which some parameters can take the discrete or integer values only (\textit{mixed-integer global 
optimization problems}) are of special interest because for these problems it is more difficult to build 
the estimates of the optimum as compared to the continuous ones.

@@

As an illustration, Fig. \ref{fig:1} presents the plots of the functions corresponding to a 
problem 
\[
%\min{\left\{ x^2 - 10\cos(2\pi x) + u^2 - 10\cos(2\pi u) : x\in [-2.22, 1.8], u \in {0,1} \right\}}
\min{\left\{ u^2 (\sin(x) +\sin(10x/3) : x\in [2.7, 7.5], u \in \{1,2\} \right\}}
\]
with one continuous parameter $x$ and one integer parameter $u$.
%Еще один график?

@@

\begin{enumerate}
	\item A continuous multiextremal function $\varphi(y), y\in D = \left\{ a_j\leq 
y_j\leq b_j, 1\leq j \leq N \right\}$ is generated with the use of the GKLS generator. The global 
minimum of this function is achieved at the known point $y'=(y'_1,...,y'_N)$ and equals 
$\varphi(y')=-1$.
	\item A concave mixed-integer function 
	\[
			h(y,u) = -2 \left[ \sum_{j=1}^N \left( \frac{y_j - y'_j}{b_j-a_j} 
\right)^2 + \sum_{j=1}^M \left( \frac{u_j - b_j}{b_j-a_j} \right)^2 \right],
	\]
	is generated where 
	\begin{gather}
	y\in D = \left\{ a_j\leq y_j\leq b_j, 1\leq j \leq N \right\} \subset R^N,\nonumber \\
	u\in U = \left\{ u_j \in  \left\{a_j, ..., b_j \right\}, 1\leq j \leq M \right\}.\nonumber
	\end{gather}
	This function has $N$ continuous and $M$ discrete parameters and achieves its 
minimum value at the point $(y',b)$.
	\item The coefficient 
	\[
	h_{max} = 4 - \min_{y,u} h(y,u) , \; y\in D, u \in U.
	\]
	is computed. 
It is obvious, that the minimum of a concave function $\mu(y,u)$ is located at one of the corner 
points of the search domain. Therefore, if the problem dimensionality is of the order of 10 it can 
be found by the brute force method.
	\item A multiextremal mixed-integer function 
	\[
	f(y,u) = \left(\varphi(y) + \sum_{j=1}^M{u_j}\right)\left(h_{max} + h(y,u)\right).
	\]
	is formed.
By construction, $f(y,u)$ would take its minimum value at the point $(y',b)$.
